### 2025-07-04 multiple-regression.qmd
20250704 - code chunk labels

```{r}
linearRegression <- lm(
  fantasyPoints ~ age + height + weight + target_share,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

@@

```{r}
newdata <- player_stats_weekly %>%
  mutate( # create a binary variable to be used as the outcome variable
    receiving_td = case_when(
      is.na(receiving_tds) ~ NA_real_, # keep NA
      receiving_tds >= 1   ~ 1,
      receiving_tds == 0   ~ 0
    )
  )

@@

```{r}
newdata <- player_stats_weekly
newdata$receiving_tdsFactor <- factor(newdata$receiving_tds, ordered = TRUE)
table(newdata$receiving_tdsFactor)

@@

```{r}
poissonRegression <- glm(
  receiving_tds ~ age + height + weight + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  family = poisson(),
  na.action = na.exclude
)

@@

```{r}
negativeBinomialRegression <- MASS::glm.nb(
  receiving_tds ~ age + height + weight + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  na.action = na.exclude,
  control = glm.control(maxit = 10000)
)

@@

@@

```{r}
summary(betaRegression)
```

>>>>

```{r}
#| label: linear-regression

linearRegression <- lm(
  fantasyPoints ~ age + height + weight + target_share,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  na.action = "na.exclude"
)

@@

```{r}
#| label: logistic-regression

newdata <- player_stats_weekly %>%
  mutate( # create a binary variable to be used as the outcome variable
    receiving_td = case_when(
      is.na(receiving_tds) ~ NA_real_, # keep NA
      receiving_tds >= 1   ~ 1,
      receiving_tds == 0   ~ 0
    )
  )

@@

```{r}
#| label: ordinal-regression

newdata <- player_stats_weekly
newdata$receiving_tdsFactor <- factor(newdata$receiving_tds, ordered = TRUE)
table(newdata$receiving_tdsFactor)

@@

```{r}
#| label: poisson-regression

poissonRegression <- glm(
  receiving_tds ~ age + height + weight + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  family = poisson(),
  na.action = na.exclude
)

@@

```{r}
#| label: negative-binomial-regression

negativeBinomialRegression <- MASS::glm.nb(
  receiving_tds ~ age + height + weight + target_share,
  data = newdata %>% filter(position %in% c("WR")),
  na.action = na.exclude,
  control = glm.control(maxit = 10000)
)

@@

```{r}
#| label: beta-regression
#| output: false

@@

```{r}
#| label: beta-regression-summmary

summary(betaRegression)
```
